---
title: parabolizR
output: html_document
always_allow_html: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("animate_play.R")
source("add_z.R")
```

The goal of this project is to interpolate the z-values for the ball from the NGS-Highlight tracking data that is available. The following is an example of the usage:

First we get the NGS highlight data using the NGS highlights library (https://github.com/asonty/ngs_highlights)

```{r get_ngs, message = FALSE}

source_url("https://raw.githubusercontent.com/asonty/ngs_highlights/master/utils/scripts/data_utils.R")
source_url("https://raw.githubusercontent.com/asonty/ngs_highlights/master/utils/scripts/plot_utils.R")
play_data <- fetch_play_data(playKey_ = 248)

```

Then we can call the `add_z()` function to add the `z` axis to a given play. 

```{r add_z}
added_z <- add_z_to_play(play_data)
```

Then we can plot the given play in two forms`three_d_animate()` or `three_d_animate_static()`. `three_d_animate()` gives us an animated frame by frame visualization of the results, and `three_d_animate_static()` gives us a static image with all of the paths rendered at once. 

```{r animate_plays, message = FALSE, warning = FALSE}
fig <- three_d_animate(added_z)
fig
```

```{r animate_static, message = FALSE, warning = FALSE}
fig <- three_d_animate_static(added_z)
fig
```